### 2019-04-10 thesis-template/msc-thesis.tex
update

This chapter will summarize the main contributions of this work studied and state targeted aims and goals as a first step in sect. \ref{sec:overview}. Then we will have a short introduction to the implemented global illumination scheme derived and simplified from an nVidia GI approach in sect. \ref{sec:scheme}. Last, we will state the effectively developed Visualization methods GIGradient and Deformation Glyphs.

@@

\section{Requirements and Ambitions}
\label{sec:spec} 
Our ambition is to develop a simple and efficient Global Illumination Propagation Scheme able to distribute energy profiles in discrete polar form in 2D/3D-space w.r.t. energy conservation and propagation attenuation principles. We opt to be compatible to handle any kind of matrix (symm./anti-symm.) and any kind of resolution of the field (full-spectrum) which leads to the conclusion that the approach should be implicitly adaptive. We then generate transmission profiles from the eigensystems (principal component frames) of the tensors for each cell in the domain (field) to provide an orientation for a grid of crystal fibre structures (cnf. optical fibres) to redirect the intensities in correspondence to the anisotropies of the tensor field. At last, we aim to generate a new FTLE-related method for tensor field vis. by applying a Global Illumination Gradient to the resulting light distributions. Our motivation is to segment key locations (LCS/ridges) in the field with tensor field lines (hyperstreamlines) converging/diverging, which is necessarily the same (for bidirectional tensor fields). Our approach should efficiently handle (relatively) large datasets. 
Knapp zwei Seiten, in dem die Anforderungen, die Zielsetzung und die
Methoden überblicksartig beschrieben werden. Hier sollte die
Beschreibung ``technischer'' bzw.~``formaler'' sein als in der
Einleitung, da der Leser nun mit den Grundlagen und verwandten
Arbeiten vertraut ist.

@@

At last, we define a threshold for the minimum overall distribution error taken into account for convergence conditions, initiating a stop sequence when falling below that threshold. As already mentioned, a dual-buffer approach is chosen here, as we can efficiently propagate from one into the other and just swap pointers to 
start all over (after reinitialization) and it yields a reasonable source-target structure.

>>>>

This chapter will summarize the main contributions of this work studied and state targeted aims and goals as a first step in sect. \ref{sec:overview}. Then we will have a short introduction to the implemented global illumination scheme derived and simplified from an nVidia GI approach in sect. \ref{sec:scheme}. Last, we will state the effectively developed Visualization methods GIGradient and Deformation Glyphs proposed as innovatively invented tensor visualization techniques.

@@

\section{Requirements and Ambitions}
\label{sec:spec} 
Our ambition is to develop a simple and efficient Global Illumination Propagation Scheme able to distribute energy profiles in discrete polar form in 2D/3D-space w.r.t. energy conservation and propagation attenuation principles. We then generate transmission profiles from the eigensystems (principal component frames) of the tensors for each cell in the domain (field). That is, to provide an orientation for a grid of crystal fibre structures (cnf. optical fibres) to redirect the intensities in analogy to the anisotropies of the tensor field within a glyph representation, obtained from Principal Component Analysis. Our approach should be implicitly adaptive to any kind of 2D dataset. Thus, we opt to be compatible to handle any kind of matrix (symm./anti-symm.) and any kind of resolution of the field (full-spectrum). At last, we aim to generate a new FTLE-related method for tensor field visualization by applying a Global Illumination Gradient to the resulting light distributions for every possible position and direction of the light source in the grid generated by stimulation with Delta-Impulses. Thus, our motivation is to segment key locations (LCS/ridges) in the field with tensor field lines (hyperstreamlines) converging/diverging, which is necessarily the same (for bidirectional tensor fields). Our approach should efficiently handle (relatively) large datasets. 
Knapp zwei Seiten, in dem die Anforderungen, die Zielsetzung und die
Methoden überblicksartig beschrieben werden. Hier sollte die
Beschreibung ``technischer'' bzw.~``formaler'' sein als in der
Einleitung, da der Leser nun mit den Grundlagen und verwandten
Arbeiten vertraut ist.

@@

At last, we define a threshold for the minimum overall distribution error taken into account for convergence conditions, initiating a stop sequence when falling below that threshold. As already mentioned, a dual-buffer approach is chosen here, as we can efficiently propagate from one into the other and just swap pointers to 
start all over (after reinitialization) and also since it yields a reasonable source-target structure. Until now we aimed to simulate the propagation of light in empty space (vacuum) providing us with a physically-motivated base-approach. We aim to modulate the transmission of the energies on top of the base approach with transmission profiles obtained from the tensor fields through Principal Component Analysis in the following.
